### 2015-10-17 locking.tex
update notation in sec 4

Consider the following simple task set consisting of two tasks on two processors that share one resource. Task $\tau_1$, on processor~1, has a total execution cost of $C_1 = 4$ and a period and deadline of $T_1 = D_1 = 8$. After one time unit of execution, jobs of $\tau_1$ require the shared resource for two time units. $\tau_1$ thus consists of two segments with costs $C_{1,1} = 1$ and $C_{1,2} = 3$. Task $\tau_2$, on processor~2, has the same overall WCET ($C_2 = 4$), a slightly shorter period ($T_2 = D_2 = 7$), and requires the shared resource for one time unit after \emph{two} time units of execution ($C_{2,1} = 2$ and $C_{2,2} = 2$). Without period enforcement (and under any reasonable locking protocol), the task set is trivially schedulable because, by construction, any job of $\tau_1$ incurs at most one time unit of blocking, and any job of $\tau_2$ incurs at most two time units of blocking.

@@

The same pattern repeats for the fourth job of $\tau_2$, released at time $21$: when its first segment ends at time $23$, the second segment is not eligible to commence execution before time $26$ since $ET_{2,4}^2 \geq ET_{2,3}^2 + T_2 = 19 + 7 = 26$. By then, however, $\tau_1$ has already locked the shared semaphore again, and the second segment of the fourth job of $\tau_2$ cannot resume before time $a^2_{2,4} = 27$, at which point
\begin{align*}
	ET_{2,4}^2 & = \max\left(ET_{2,3}^2 + T_2,\ \mathit{busy}(\tau_2, a^2_{2,4})\right) =\max(26,\ 27) = 27.
\end{align*}
However, this leaves insufficient time to meet the job's deadline: as the second segment of $\tau_2$ requires $C_{2,2} = 2$ time units to complete, the job's deadline at time~$28$ is  missed.

@@

To this end, consider two tasks with identical parameters hosted on two processors. Task $\tau_1$ is hosted on processor~1; task $\tau_2$ is hosted on processor~2. Both tasks have the same period and relative deadline $T_1 = T_2 = D_1 = D_2 = 8$ and the same WCET of $C_1 = C_2 = 4$. They both access a single shared resource for two time units each per job. Both tasks request the shared resource after executing for \emph{at most} one time unit. They both thus have two segments each with parameters $C_{1,1} = C_{2,1} = 1$ and $C_{1,2} = C_{2,2} = 3$.

>>>>

Consider the following simple task set consisting of two tasks on two processors that share one resource. Task $\tau_1$, on processor~1, has a total execution cost of $C_1 = 4$ and a period and deadline of $T_1 = D_1 = 8$. After one time unit of execution, jobs of $\tau_1$ require the shared resource for two time units. $\tau_1$ thus consists of two segments with costs $C_1^1 = 1$ and $C_1^2 = 3$. Task $\tau_2$, on processor~2, has the same overall WCET ($C_2 = 4$), a slightly shorter period ($T_2 = D_2 = 7$), and requires the shared resource for one time unit after \emph{two} time units of execution ($C_2^1 = 2$ and $C_2^2 = 2$). Without period enforcement (and under any reasonable locking protocol), the task set is trivially schedulable because, by construction, any job of $\tau_1$ incurs at most one time unit of blocking, and any job of $\tau_2$ incurs at most two time units of blocking.

@@

The same pattern repeats for the fourth job of $\tau_2$, released at time $21$: when its first segment ends at time $23$, the second segment is not eligible to commence execution before time $26$ since $ET_{2,4}^2 \geq ET_{2,3}^2 + T_2 = 19 + 7 = 26$. By then, however, $\tau_1$ has already locked the shared semaphore again, and the second segment of the fourth job of $\tau_2$ cannot resume before time $a^2_{2,4} = 27$, at which point
\begin{align*}
	ET_{2,4}^2 & = \max\left(ET_{2,3}^2 + T_2,\ \mathit{busy}(\tau_2, a^2_{2,4})\right) =\max(26,\ 27) = 27.
\end{align*}
However, this leaves insufficient time to meet the job's deadline: as the second segment of $\tau_2$ requires $C_2^2 = 2$ time units to complete, the job's deadline at time~$28$ is  missed.

@@

To this end, consider two tasks with identical parameters hosted on two processors. Task $\tau_1$ is hosted on processor~1; task $\tau_2$ is hosted on processor~2. Both tasks have the same period and relative deadline $T_1 = T_2 = D_1 = D_2 = 8$ and the same WCET of $C_1 = C_2 = 4$. They both access a single shared resource for two time units each per job. Both tasks request the shared resource after executing for \emph{at most} one time unit. They both thus have two segments each with parameters $C_1^1 = C_2^1 = 1$ and $C_1^2 = C_2^2 = 3$.
